---
title: "p8105_hw1_mf3593"
author: "Miao Fu"
date: "2023-09-18"
output: github_document
---

I'm an R Markdown document! 

#Problem 1
```{r}
library(moderndive)
library(tidyverse)
data("early_january_weather")
ggplot(early_january_weather, aes(x=time_hour,y=temp,color=humid))+geom_point()
ggsave("early_january_weather.pdf")
```
the dataset contains weather information for EWR in January of the year 2013. It has variables `r colnames(early_january_weather)`. It records temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib every hour on every day for fifteen days in January 2013. The size of the dataset is `r nrow(early_january_weather)` rows `r ncol(early_january_weather)` columns. The mean temperature is `r mean(early_january_weather[["temp"]])`

According to the scatterplot of this dataset, we can see the temperature fluctuates a lot within one day but overall increased from Jan 01 to Jan 15. The humidity also in general increased over the 15 days. 

#Problem 2

```{r}
df=tibble(
  x=rnorm(10),
  log_vec=x>0,
  cha_vec=c("A","B","C","D","E","F","G","H","I","J"),
  fac_vec=factor(c("Low","Medium","Medium","High","Low","Medium","High","High","Low","High"))
)
mean_x=mean(pull(df,x))
mean_log=mean(pull(df,log_vec))
mean_cha=mean(pull(df,cha_vec))
mean_fac=mean(pull(df,fac_vec))
```
when calculating mean, mean function works for x and mean_log, but mean_cha and mean_fac return NA and a warning message shows argument is not numeric or logical: returning NA. 

```{r, echo=TRUE, eval=FALSE}
as.numeric(pull(df,log_vec))
as.numeric(pull(df,cha_vec))
as.numeric(pull(df,fac_vec))
```

when apply as.numeric, the factor vector is converted to numeric vector. The logical vector can be converted based on 1 corresponds to TRUE and 0 corresponds to FALSE. The factor vector can be converted to numeric factor where numeric codes corresponding to the factor levels are returned. Character vector is converted only when the original content is a number but in character format. In this case, since it was letters, it was not converted to numeric vector. This explains why we couldn't get mean of factor and character vectors before. We need to convert them to numeric values.

