---
title: "p8105_hw1_mf3593"
author: "Miao Fu"
date: "2023-09-18"
output: html_document
---

I'm an R Markdown document! 

#Problem 1
```{r}
library(moderndive)
library(tidyverse)
data("early_january_weather")
ggplot(early_january_weather, aes(x=time_hour,y=temp,color=humid))+geom_point()
ggsave("early_january_weather.pdf")
```
the dataset contains weather information for EWR in January of the year 2013. It has variables `r colnames(early_january_weather)`. It records temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib every hour on every day for fifteen days in January 2013. The size of the dataset is `r nrow(early_january_weather)` rows `r ncol(early_january_weather)` columns. The mean temperature is `r mean(early_january_weather[["temp"]])`

According to the scatterplot of this dataset, we can see the temperature fluctuates a lot within one day but overall increased from Jan 01 to Jan 15. The humidity also in general increased over the 15 days. 

#Problem 2

```{r}
df=tibble(
  x=rnorm(10),
  log_vec=x>0,
  cha_vec=c("1","2","3","4","5","6","7","8","9","10"),
  fac_vec=factor(c("Low","Medium","Medium","High","Low","Medium","High","High","Low","High"))
)
```